\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-17 manuscript.tex
* table 1 updated

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}}
\caption{\label{tab:unnamed-chunk-2}Releated Scales}\\
\toprule
Name & Author & Description & Relevant Items\\
\midrule
\endfirsthead
\caption[]{\label{tab:unnamed-chunk-2}Releated Scales \textit{(continued)}}\\
\toprule
Name & Author & Description & Relevant Items\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & NA\\
Office Light Survey & Eklundet al., 1996 & A survey to assess electrical lighting environment in office & NA\\
Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & Self-administered semi-quantitative light questionnaire & NA\\
Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & NA\\
Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & NA\\
\addlinespace
Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & NA\\
Assessment of Sleep Environment & Olivier et.al., 2016 & 13 items questionnaire measuring your sleep environment quality & NA\\
The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & NA\\
Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,22-25 and 29\\
Photosensitivity Assessment Questionnaire (PAQ) & Wu et al., 2017 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms\\*
\end{longtable}

@@

Figure \ref{fig:FlowchartFig} summarizes the steps of our psychometric analysis. For our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information. As such we decided to collapse them into one making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (PA) as factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by another factor extraction method: ``the minimum residuals extraction'' as well. We used a combination of factor identification method including scree plot (Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method (Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018). We confirmed the latent structure obtained in the EFA by conducting a ``Confirmatory Factor Analysis'' (CFA) using ``robust weighted least square estimator'' (WLSMV). We estiablished the measurement invariance of our tool across native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to ``Semantic Scale Network'' (Rosenbusch, Wanders, \& Pit, 2020). Lastly, we sought ``Item Response Theory'' (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \ref{tab:EFATableAppB}) and rejected the latent structure obtained as the factors were less interpretable.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \ref{tab:MinResTab}). Table \ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from .49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. Figure \ref{fig:EFAplot} depicts the obtained five-five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \ref{fig:EFAResiduals}) showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (Desjardins \& Bulut, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \ref{tab:sixFacTab}).

@@

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}

>>>>

\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}}
\caption{\label{tab:unnamed-chunk-2}Releated Scales}\\
\toprule
Name & Author & Description & Relevant Items to capture light exposure related behavior & Scale type & Validity evidences\\
\midrule
\endfirsthead
\caption[]{\label{tab:unnamed-chunk-2}Releated Scales \textit{(continued)}}\\
\toprule
Name & Author & Description & Relevant Items to capture light exposure related behavior & Scale type & Validity evidences\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & None & 5-point Likert scale & Not available\\
Office Light Survey & Eklundet al., 1996 & 30 items survey to assess electrical lighting environment in office & Item 29 & Mixed response format & Not available\\
Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & 1 item semi-quantitative light questionnaire & none & Semi-quantitative & NA\\
Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & Item 16,17 & 5-point Likert scale & Face and Content validity\\
Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & item 1,2,8,13,14 & Mixed response format & Correlation of total score and the oral temperature\\
\addlinespace
Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & Time spect outdoors & Mixed response format & Correlation between  total score and sleep-logs, actimetry, physiological parameters\\
 Sleep Practices and Attitudes Questionnaire (SPAQ) & Olivier et.al., 2016 & 16 Factor questionnaire measuring practice, behavior and attitude related sleep & Subscale 8\&9 & 5-point Likert scale & Face and Construct validity\\
The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & item 1-4 & Mixed response format & Correlation of total score with clinical measurements\\
Self-Rating of Biological Rhythm Disorder for Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,6,22-25 and 29 & 5-point Likert scale & Construct validity\\
Photosensitivity Assessment Questionnaire (PAQ) & Bossini et al.,2006 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms & Binary response option & NA\\*
\end{longtable}

@@

Figure \ref{fig:FlowchartFig} summarizes the steps of our psychometric analysis. In our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always). Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information. As such we decided to collapse them into one, making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA. We employed principal axis (PA) as factor extraction method with varimax rotation. PA is robust to the normality assumption violations (Watkins, 2020). The obtained latent structure was confirmed by another factor extraction method: ``the minimum residuals extraction'' as well. We used a combination of factor identification method including scree plot (Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method (Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers. Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018). We confirmed the latent structure obtained in the EFA by conducting a categorical ``Confirmatory Factor Analysis'' (CFA) using ``robust weighted least square estimator'' (WLSMV). We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework. To assess the possible semantic overlap of our tool with the existing tools, we sought to ``Semantic Scale Network'' (Rosenbusch, Wanders, \& Pit, 2020). Lastly, we sought ``Item Response Theory'' (IRT) based analysis on developing a short form of LEBA.
We also conducted psychometric analysis on non-merged response options data (Supp. Table \ref{tab:EFATableAppB}) and rejected the latent structure obtained as the factors were less interpretable.

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \ref{tab:MinResTab}). Table \ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from .49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. Figure \ref{fig:EFAplot} depicts the obtained five-five factor structure. However, the histogram of the absolute values of non-redundant residual-correlations (Figure \ref{fig:EFAResiduals}) showed 26\% correlations were greater than the absolute value of .05, indicating a possible under-factoring. (Desjardins \& Bulut, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \ref{tab:sixFacTab}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-bossini2006sensibilita}{}}%
Bossini, L., Valdagno, M., Padula, L., De Capua, A., Pacchierotti, C., \& Castrogiovanni, P. (2006). Sensibilit{à} alla luce e psicopatologia: Validazione del questionario per la valutazione della fotosensibilit{à} (QVF). \emph{Med Psicosomatica}, \emph{51}, 167--176.

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
\end{minipage} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}

\hypertarget{geographic-locations-of-survey-participants}{%
\section{Geographic Locations of Survey
Participants}\label{geographic-locations-of-survey-participants}}

\caption{\label{tab:TzTable}Geographical Location}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ll}
\toprule
 & N = 690\\
\midrule
Time zone - Country & \\
\hspace{1em}United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
\hspace{1em}United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
\hspace{1em}Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
\hspace{1em}India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
\addlinespace
\hspace{1em}United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
\hspace{1em}United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
\hspace{1em}France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
\hspace{1em}Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
\hspace{1em}Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
\addlinespace
\hspace{1em}Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
\hspace{1em}Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
\hspace{1em}Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
\hspace{1em}Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
\hspace{1em}Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
\addlinespace
\hspace{1em}Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
\hspace{1em}Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
\hspace{1em}Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
\hspace{1em}Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
\hspace{1em}China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
\addlinespace
\hspace{1em}Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
\hspace{1em}Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
\hspace{1em}United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
\hspace{1em}Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
\hspace{1em}New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
\addlinespace
\hspace{1em}Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
\hspace{1em}Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
\hspace{1em}United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
\hspace{1em}United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
\hspace{1em}Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
\addlinespace
\hspace{1em}Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
\hspace{1em}Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
\hspace{1em}Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
\hspace{1em}South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
\hspace{1em}Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
\addlinespace
\hspace{1em}Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
\hspace{1em}Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
\hspace{1em}Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
\hspace{1em}United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
\hspace{1em}Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
\addlinespace
\hspace{1em}Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
\hspace{1em}Iran & 3 (0.4\%)\\
\hspace{1em}Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
\addlinespace
\hspace{1em}Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
\hspace{1em}Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
\hspace{1em}Taiwan & 3 (0.4\%)\\
\addlinespace
\hspace{1em}United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
\hspace{1em}United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
\hspace{1em}United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
\hspace{1em}Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
\hspace{1em}Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
\hspace{1em}Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
\hspace{1em}Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
\hspace{1em}Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
\hspace{1em}Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
\hspace{1em}Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
\hspace{1em}Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
\hspace{1em}Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
\hspace{1em}Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
\hspace{1em}Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
\hspace{1em}Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
\hspace{1em}Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
\hspace{1em}Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
\hspace{1em}Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
\hspace{1em}Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
\hspace{1em}Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
\hspace{1em}Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
\addlinespace
\hspace{1em}Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
\hspace{1em}United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
\hspace{1em}United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
\hspace{1em}Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
\hspace{1em}Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
\hspace{1em}Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
\hspace{1em}Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
\hspace{1em}Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
\hspace{1em}Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
\hspace{1em}Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
\hspace{1em}Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
\hspace{1em}Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
\hspace{1em}Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
\hspace{1em}Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
\hspace{1em}Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
\hspace{1em}Macedonia & 1 (0.1\%)\\
\hspace{1em}Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
\hspace{1em}Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
\hspace{1em}Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
\hspace{1em}New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
\hspace{1em}Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
\hspace{1em}Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
\hspace{1em}Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
\hspace{1em}Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
\hspace{1em}Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
\hspace{1em}Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
\hspace{1em}Tanzania & 1 (0.1\%)\\
\addlinespace
\hspace{1em}Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
\hspace{1em}United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
\hspace{1em}Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
\hspace{1em}Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
\hspace{1em}American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
\hspace{1em}Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
\addlinespace
\hspace{1em}Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
\hspace{1em}Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
\hspace{1em}Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
\hspace{1em}Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
\hspace{1em}Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
\hspace{1em}Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Bonaire & 0 (0\%)\\
\addlinespace
\hspace{1em}Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
\hspace{1em}Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
\hspace{1em}Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
\hspace{1em}British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
\hspace{1em}Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
\addlinespace
\hspace{1em}Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
\hspace{1em}Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
